Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-01 article.qmd
Improve the legend of the performance

![Performance of the different softwares to solve a subset of BioModels models. (left) Run time for model BIOMD3 as a function of the number of output points. (right) Run time for different models ordered according to the geometric mean of the run times, using 300 output points.](src/performance/figures/performance.png){#fig-runtime}

>>>>

![Performance of different softwares to solve models from the cureted section of BioModels. (left) Run time for the model BIOMD3 as a function of the number of output points. (right) Run time for different models for 300 output points, using the geometric mean of the different softwares to order them.](src/performance/figures/performance.png){#fig-runtime}
